---
title: "Index of accumulation-depuration data collection in support of toxicokinetic modelling for testing in MOSAIC~bioacc~"
author: "Aude Ratier & Sandrine Charles"
date: "`r Sys.Date()`"
urlcolor: orange
linkcolor: orange
citecolor: orange
output: 
bookdown::html_document2:
toc: FALSE
bibliography: mybib.bib
csl: american-chemical-society.csl
option: -\usepackage{lscape} -\usepackage{xcolor}     - \usepackage {hyperref}   - \usepackage{fancyhdr}
    - \hypersetup {colorlinks = true, linkcolor = orange, urlcolor = orange}
header-includes:
    - \usepackage{xcolor}
    - \usepackage{ulem}
    - \usepackage{fancyhdr}
    # - \usepackage{fontspec}
---


\fontsize{12}{22}
\pagestyle{fancyplain}
\rhead{\includegraphics[height=1cm]{logo_bioacc.png}}
\lhead{\includegraphics[height=1cm]{logo_2.png}}


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, dpi = 300)
```

```{=html}
<style type="text/css">
.main-container {
  max-width: 90%;
  margin-left: auto;
  margin-right: auto;
}
h2 {
    color: orange;
}
.markdown-block a {
    color: orange !important;
}
</style>
```
\newcommand{\blandscape}{\begin{landscape}}

```{r fig-margin, echo = FALSE, align="right"}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,...)
    )
}
image_link("logo_bioacc.png","http://mosaic.univ-lyon1.fr/bioacc",width="70px",align="right")
```

```{r , include = FALSE}

# Working directory ####
# setwd("~/Seafile/ANSES-bioacc/DATA-TESTS/UPDATE/archivage_index_dataset")
 path <- "www/data/database/"
# path of all data sets ####
# pathdata <-  "~/Seafile/ANSES-bioacc/DATA-TESTS/UPDATE/archivage_index_dataset/dataset/"
pathdata <- "www/data/database/dataset/"
# path for all reports ####
# pathreport <- "~/Seafile/ANSES-bioacc/DATA-TESTS/UPDATE/archivage_index_dataset/reports/"
pathreport <- "www/data/database/reports/"

# Packages ####
library(stringr)
library(RefManageR)
library(bibtex)
library(htmltools)
library(readr)
library(dplyr)
library(DT)
```

## Indroduction

This database contains a wide collection of raw data sets extracted from the scientific literature in support of TK modelling to be performed with the MOSAIC\textsubscript{bioacc} web application (<https://mosaic.univ-lyon1.fr/bioacc/>). More details on the database are given in the [companion paper](https://www.biorxiv.org/content/10.1101/2021.04.15.439942v1).

All data sets are summarized by:\
- the name of the file of the data set (directly downloadable)\
- the organism tested (genus)\
- the category of the organism (*e.g.* aquatic, terrestrial, etc.)\
- the substance tested\
- the time at the end of the accumulation phase ($t_{acc}$)\
- the exposure route tested and for which we have data (*e.g.* water, sediment, food, pore water)\
- the total number of data in the dataset (number of replicate(s))\
- the kinetic bioaccumulation factor median value with its 95% credible intervals\
- the report in .pdf (directly downloadable)\
- the reference or source of the data set\
- possible comments added (*e.g.* lipid fraction, growth, biotransformation)\

## Your contribution

If you want to contribute to this database in sharing your raw TK data, please contact us at [sandrine.charles\@univ-lyon1.fr](mailto:sandrine.charles@univ-lyon1.fr).

## Database

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
if(file.exists("model.txt")) file.remove("model.txt")
dataset = NULL
file.name = NULL # gives the name files without format (.txt or .csv)
files.reports = NULL
species = NULL
substance = NULL
report = NULL
reference = NULL
duration = NULL
comments = NULL
exposure = NULL
replicate = NULL
colname = NULL
met = NULL
data = NULL
npoint = NULL
Cexp = NULL
factor.conc = NULL
l.fac.conc = NULL
test = NULL
npoints = NULL
category = NULL
tacc1 = NULL
timeFormat1 = NULL
# path of all data sets ####
files <- list.files(pattern = ".csv") # file names
files <- c(files, list.files(pattern = ".txt"))
files <- sort(files) #reorder in alphabetic
files <- files[-c(4:6,24)]

ndata <- length(files) # number of data set
# For windows, using PowerShell, rename all files by using: (do not forget to be in the good working directory)
# cd C:/Users/Aude/documents/MOSAIC_BIOACC/DATA-TESTS/UPDATE/archivage_index_dataset/reports/ # working directory for PowerShell
# get-childitem *.pdf | foreach { rename-item $_ $_.Name.Replace("2021-03-18_", "") }

for (i in 1:ndata){
  file.name[i] <-  str_replace_all(files[i], ".txt","")
  file.name[i] <-  str_replace_all(file.name[i], ".csv","")
  files.reports[i] <-list.files(pattern = paste0(file.name[i],".pdf")) # file names for report
}

files.reports <- unique(files.reports) #select only one file name report if duplicate

# separate information available in the name file
names <- sapply(file.name, function(x) str_split(x, "_"))


# REFERENCES ####
# browse references
# setwd(path)
bib <- ReadBib(file = "mybib.bib")
# BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
for (i in 1:ndata){
     reference[i] <- c(names[[i]][4])
   # reference[i] <- paste0("[@", reference[i],"]")
     reference[i] <- RefManageR::TextCite(bib = bib,
                                            paste0(reference[i]),
                                            .opts = list(style = "html",
                                                        max.names = 1, longnamesfirst=FALSE))


     reference[i] <- str_replace(reference[i], ", et al.", HTML("<i> et al.</i>"))

     reference[i] <- str_replace(reference[i], "'>", paste0("'target='_blank'>"))
   # reference[i] <- paste0("<a href='#references'>",reference[i],"</a>")
}


# SPECIES, SUBSTANCE, DURATION, REPORT LINK, COMMENTS ####
for (i in 1:ndata){
  dataset[i] <- paste0("<a href='", files[i],"'target='_blank'>",files[i],"</a>")
  species[i] <- names[[i]][1]
  substance[i] <- c(names[[i]][2])
  duration[i] <- c(names[[i]][3])
    duration[i] <-  str_replace(duration[i], "y"," years")
    duration[i] <-  str_replace(duration[i], "h"," hours")
    duration[i] <-  str_replace(duration[i], "d"," days")
    duration[i] <-  str_replace(duration[i], "w"," weeks")

  report[i] <- paste0("<a href='", files.reports[i],"' target='_blank'>Link</a>")
}

# collect only tacc value
for (i in 1:ndata){
	tacc1[i] <- duration[i]
    tacc1[i] <-  str_remove_all(tacc1[i]," years")
    tacc1[i] <-  str_remove_all(tacc1[i], " hours")
    tacc1[i] <-  str_remove_all(tacc1[i], " days")
    tacc1[i] <-  str_remove_all(tacc1[i]," weeks")
}
tacc1 <- as.numeric(tacc1)

# Create time units vector

for (i in 1:ndata){
    if(str_detect(duration[i],"years")==TRUE){timeFormat1[i] <-"years"}
    if(str_detect(duration[i],"hours")==TRUE){timeFormat1[i] <-"hours"}
    if(str_detect(duration[i],"days")==TRUE){timeFormat1[i] <- "days"}
    if(str_detect(duration[i],"week")==TRUE){timeFormat1[i] <- "week"}
}

 # EXPOSURE ROUTE ####
    #read exposure route in data set

    # All dataset in a list
for (i in 1:ndata){
  # setwd(path)
  if(str_detect(files[i],".csv")){data[[i]] <-  read_delim(files[i],
                                                     delim = ";",
                                                     col_types = cols(),
                                                     escape_double = FALSE,
                                                     trim_ws = FALSE)}
  if(str_detect(files[i],".txt")){data[[i]] <- read_delim(files[i],
                                                      delim = "\t",
                                                      escape_double = FALSE, trim_ws = TRUE)}

  # select exposure route
 colname[[i]] <- colnames(data[[i]])

  if("expw" %in% colname[[i]]){exposure[[i]] <- c("water") }
    if("exppw" %in% colname[[i]]){exposure[[i]] <- c("pore water") }
      if("exps" %in% colname[[i]]){exposure[[i]] <- c("sediment") }
      if("expf" %in% colname[[i]]){exposure[[i]] <- c("food") }
  exposure <- unlist(exposure)



 # NUMBER OF POINTS ####
   # replicate
replicate[i] <- length(unique(data[[i]]$replicate)) #add condition by exp concentration
	 # concentration of exposure
  Cexp[[i]] <- data[[i]] %>%
		filter_all(any_vars(! is.na(.))) %>%
		filter(time != 0) %>%
		select(starts_with("exp"))

temp.Cexp <- data.frame(Cexp[[i]]) #temporary data frame instead of tibble for Cexp
factor.conc[[i]] <- levels(factor(temp.Cexp[,1])) #levels of exposure concentration


npoints[i] <- nrow(Cexp[[i]] %>% filter(Cexp[[i]] == factor.conc[[i]][1]))
npoint[i] <- paste0(npoints[i], " (",replicate[i],")")

 #add comments
  comments[i] <- c(names[[i]][5])
    # comments[i] <- str_replace_all(comments[i], "conc"," tested concentrations") #length(unique(Cexp)) or as.factor(Cexp)

   if("growth" %in% colnames(data[[i]])){comments[i] <- paste0(comments[i], "growth dilution")}

  # Metabolites ? ####
if("concm1" %in% colnames(data[[i]])){comments[i] <- paste0(comments[i],"biotransformation")} #number of metabolites?
  comments[i] <- str_replace_all(comments[i], "intermediate","intermediate size")
  comments[i] <- str_replace_all(comments[i], "small","small size")
  comments[i] <- str_replace_all(comments[i], "food","")
  comments[i] <- str_replace_all(comments[i], "sediment","")
  comments[i] <- str_replace_all(comments[i], "lipid","lipid fraction: 6.8%")
    # comments[i] <- str_replace_all(comments[i], "conc"," tested concentrations")
 if(length(factor.conc[[i]]) > 1){comments[i] <- paste0(comments[i], length(factor.conc[[i]])," tested concentrations")}

comments[i] <- str_replace_all(comments[i], "NA","")
}

 # CATEGORY ####
factor <- lapply(factor(species), levels)[[1]] # give all species
for (i in 1:ndata){
if("Asellus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Axinella" %in% species[i]){category[i] <- c("seawater sponge")}
if("Calanus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Chaetopteryx" %in% species[i]){category[i] <- c("insect")}
if("Chironomus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Chlorella" %in% species[i]){category[i] <- c("aquatic algae")}
if("Danio" %in% species[i]){category[i] <- c("fish")}
if("Daphnia" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Eisenia" %in% species[i]){category[i] <- c("aquatic worm")}
if("Ephemera" %in% species[i]){category[i] <- c("insect")}
if("Gammarus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Halophila" %in% species[i]){category[i] <- c("seawater plant")}
if("Heptagenia" %in% species[i]){category[i] <- c("insect")}
if("Hyalella" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Hydropsyche" %in% species[i]){category[i] <- c("insect")}
if("Lumbriculus" %in% species[i]){category[i] <- c("aquatic worm")}
if("Oncorhynchus" %in% species[i]){category[i] <- c("fish")}
if("Oryzias" %in% species[i]){category[i] <- c("fish")}
if("Physa" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Poecilus" %in% species[i]){category[i] <- c("insect")}
if("Radix" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Snail" %in% species[i]){category[i] <- c("terrestrial invertebrate")}
if("Solea" %in% species[i]){category[i] <- c("fish")}
if("Tubifex" %in% species[i]){category[i] <- c("aquatic worm")}
if("Planorbarius" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Enchytraeus" %in% species[i]){category[i] <- c("terrestrial worm")}

}
```

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
# fitPlot = NULL
# BAF.name <- NULL
# BAF50 <- NULL
# BAF2.5 <- NULL
# BAF97.5 <- NULL
# 
# for (x in 90:ndata){
# # filename <- files[i]
# # dataTable <- as_tibble(data[[i]])
# # tacc <- tacc1[i]
# # timeFormat <- timeFormat1[i] # Time unit
# source("model_predict.r")
# a <- print(paste0("Coffee is life!", x)) # to check the loop
# 		#generate the report
# 	# Variables for report
# 	concFileName <- files[x]
# 	nbReplicates <- as.numeric(replicate[x])
# 	# knit in format .PDF
# 	rmarkdown::render(input = "reportBIOACC_pdf.Rmd",
#             output_format = "pdf_document")
# a <- print(paste0("Hot coffee!", x)) # to check the loop
# 	file.rename(from="reportBIOACC_pdf.pdf",
#               to=paste("reports/", file.name[x],".pdf", sep=""))
#   # knit in format .HTML
# 	rmarkdown::render(input = "reportBIOACC_pdf.Rmd",
#             output_format = "html_document")
# 	print(paste0("Hot coffee!", x))
# 	file.rename(from="reportBIOACC_pdf.html",
#               to=paste("reports/", file.name[x],".html", sep=""))
# 	
# 	
# 		if("exppw" %in% colnames(dataTable)){BAF.name[x] <- paste0("BCFpw")
# BAF50[x] <- bcfpwMed
# BAF2.5[x] <- 	bcfpwInf
# BAF97.5[x] <- 	bcfpwSup
# 		}
# 	if("expw" %in% colnames(dataTable)){BAF.name[x] <- paste0("BCF")
# BAF50[x] <- bcfMed
# BAF2.5[x] <- bcfInf	
# BAF97.5[x] <-bcfSup
# 	}
# 	if("exps" %in% colnames(dataTable)){BAF.name[x] <- paste0("BSAF")
# BAF50[x] <- bsafMed
# BAF2.5[x] <- bsafInf	
# BAF97.5[x] <- bsafSup
# 	}
# 	if("expf" %in% colnames(dataTable)){BAF.name[x] <- paste0("BMF")
# BAF50[x] <- bmfMed
# BAF2.5[x] <- bmfInf	
# BAF97.5[x] <- bmfSup
# 	}
# 
# }

# BAF.table <- as.data.frame(cbind(BAF.name,BAF50,BAF2.5,BAF97.5))
# write.csv(BAF.table,"BAF_table.csv", row.names = FALSE)

# BAF
# BAF <- NULL
# BAF.table <- read_delim("baf.txt", "\t", escape_double = FALSE,
#     col_types = cols(median = col_number(),
#         `2,5` = col_number(), `97,5` = col_number()),
#     trim_ws = TRUE)
# for (i in 1:length(file.name)){
#   BAF[i] <- HTML(paste0(BAF.table[i,2]), "</br>", paste0("[",BAF.table[i,3]," - ",BAF.table[i,4],"]"))
# }
# write.csv(BAF,"BAF.csv", row.names = FALSE)

library(readr)
BAF <- as.data.frame(read_csv("BAF.csv"))
BAF <- BAF[,1]

```

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
#create the data frame
datatable <- NULL
datatable <- cbind.data.frame(dataset,paste0("<i>",species,"</i>"),  category, substance, duration, exposure, npoint, BAF, report, reference, comments)
colnames(datatable)<-c("dataset","genus","category", "substance", "duration of accumulation", "exposure route", "n (replicate)","Kinetic biaccumulation factor", "report", "reference", "comments")

 # write.csv(datatable,"datatable.csv", row.names = FALSE)

# View(data)

```

```{r echo=FALSE}
# datatable <- read_csv("datatable.csv")
# save(datatable,file="save")
# load("save")
DT::datatable(datatable, escape = FALSE, rownames = FALSE, options = list(
  pageLength=10,fixedHeader = TRUE, fixedHeader.header = TRUE, columnDefs =
                           list(list(className = 'dt-center',
                                     targets = 1:9))), extensions = 'FixedHeader')
# datatable <<- datatatable
# datatable(datatable, class = 'cell-border stripe')

```

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
# library(kableExtra)
# kbl(data) %>%
#   kable_paper() %>%
#   scroll_box(width = "200%", height = "200px")

```

<!-- ## References -->

```{r results = "asis", echo = FALSE, warning=FALSE}
# PrintBibliography(bib, .opts = list(check.entries = FALSE, sorting = "anyt"))
```
