---
title: "Accumulation-depuration data collection in support of toxicokinetic modelling"
author: "Aude Ratier & Sandrine Charles"
date: "`r Sys.Date()`"
urlcolor: orange
linkcolor: orange
citecolor: orange
output: 
bookdown::html_document2:
toc: FALSE
bibliography: mybib.bib
csl: american-chemical-society.csl
option: -\usepackage{lscape} -\usepackage{xcolor}     - \usepackage {hyperref}   - \usepackage{fancyhdr}
    - \hypersetup {colorlinks = true, linkcolor = orange, urlcolor = orange}
header-includes:
    - \usepackage{xcolor}
    - \usepackage{ulem}
    - \usepackage{fancyhdr}
 # - \usepackage{fontspec}
---



```{=tex}
\fontsize{12}{22}
\pagestyle{fancyplain}
\rhead{\includegraphics[height=1cm]{logo_bioacc.png}}
\lhead{\includegraphics[height=1cm]{logo_2.png}}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, dpi = 300)
```

```{=html}
<style type="text/css">
.main-container {
  max-width: 90%;
  margin-left: auto;
  margin-right: auto;
}
h2 {
    color: orange;
}
.markdown-block a {
    color: orange !important;
}
</style>
```
\newcommand{\blandscape}{\begin{landscape}}

```{r fig-margin, echo = FALSE, align="right"}
image_link <- function(image,url,...){
  htmltools::a(
    href=url,
    htmltools::img(src=image,...)
    )
}
image_link("logo_bioacc.png","http://mosaic.univ-lyon1.fr/bioacc",width="70px",align="right")
```

```{r , include = FALSE}

# Working directory ####
 path <- "www/data/database/"
# path of all data sets ####
pathdata <- "www/data/database/new/"
# path for all reports ####
pathreport <- "www/data/database/reports/"

# Packages ####
library(stringr)
library(RefManageR)
library(bibtex)
library(htmltools)
library(readr)
library(dplyr)
library(DT)

```

## Introduction

This database contains a wide collection of raw data sets extracted from the scientific literature in support of TK modelling which can be performed with the MOSAIC\textsubscript{bioacc} web application (<https://mosaic.univ-lyon1.fr/bioacc/>).

More details on the database are given in the [companion paper](https://www.biorxiv.org/content/10.1101/2021.04.15.439942v1).

All data sets are summarized by:

+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+
| \- the name of the file of the data set (directly downloadable)                                    | \- the total number of data in the dataset (number of replicate(s))                |
+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+
| \- the organism tested (genus)                                                                     | \- the kinetic bioaccumulation factor median value with its 95% credible intervals |
+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+
| \- the category of the organism (*e.g.* aquatic, terrestrial, etc.)                                | \- the report in .pdf (directly downloadable)                                      |
+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+
| \- the substance tested                                                                            | \- the reference or source of the data set                                         |
+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+
| \- the time at the end of the accumulation phase ($t_{acc}$)                                       | \- possible comments added (*e.g.* lipid fraction, growth, biotransformation)      |
+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+
| \- the exposure route tested and for which we have data (*e.g.* water, sediment, food, pore water) |                                                                                    |
+----------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------+

## Your contribution

If you want to contribute to this database in sharing your raw TK data, please contact us at [sandrine.charles\@univ-lyon1.fr](mailto:sandrine.charles@univ-lyon1.fr).

## Database

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
if(file.exists("model.txt")) file.remove("model.txt")
dataset = NULL
file.name = NULL # gives the name files without format (.txt or .csv)
files.reports = NULL
species = NULL
substance = NULL
report = NULL
reference = NULL
duration = NULL
comments = NULL
exposure = NULL
replicate = NULL
colname = NULL
met = NULL
data = NULL
npoint = NULL
Cexp = NULL
factor.conc = NULL
l.fac.conc = NULL
test = NULL
npoints = NULL
category = NULL
tacc1 = NULL
timeFormat1 = NULL

############################################################
######## UPLOAD OLD DATABASE AND ADD NEW FILES #############
############################################################
# Upload the dataframe already in a good format and calculations performed
# datatable_old <- read_csv("datatable_update.csv")

  # path of all data sets ####

files <- list.files(pattern = ".csv") # file names
files <- c(files, list.files(pattern = ".txt"))
files <- sort(files) #reorder in alphabetic
ndata <- length(files)

for (i in 1:ndata){
  file.name[i] <-  str_replace_all(files[i], ".txt","")
  file.name[i] <-  str_replace_all(file.name[i], ".csv","")
}

# path of reports ####
 files.reports <- NULL
for(i in 1:ndata){ #change to update, go to 1:67 for version 2.0
files.reports[i] <-	list.files(pattern = paste0(file.name[i],".pdf"))
# if(str_detect(datatable_old[,1],files.reports[i])==TRUE) files.reports[i] <- files[-i]
}
files.reports <- unique(files.reports) #select only one file name report if duplicate


# separate information available in the name file
names <- sapply(file.name, function(x) str_split(x, "_"))


# # REFERENCES ####
# browse references
# setwd(path)
bib <- ReadBib(file = "mybib.bib")
 # BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
for (i in 1:ndata){
     reference[i] <- c(names[[i]][4])
   # reference[i] <- paste0("[@", reference[i],"]")
     reference[i] <- RefManageR::TextCite(bib = bib,
                                            paste0(reference[i]),
                                            .opts = list(style = "html",
                                                        max.names = 1, longnamesfirst=FALSE))


     reference[i] <- str_replace(reference[i], ", et al.", HTML("<i> et al.</i>"))

     reference[i] <- str_replace(reference[i], "'>", paste0("'target='_blank'>"))
   # reference[i] <- paste0("<a href='#references'>",reference[i],"</a>")
}


# SPECIES, SUBSTANCE, DURATION, REPORT LINK, COMMENTS ####
for (i in 1:ndata){
dataset[i] <- paste0("<a href='", files[i],"'target='_blank'>",files[i],"</a>")
species[i] <- names[[i]][1]
substance[i] <- c(names[[i]][2])
duration[i] <- c(names[[i]][3])
  duration[i] <-  str_replace(duration[i], "y"," years")
  duration[i] <-  str_replace(duration[i], "h"," hours")
  duration[i] <-  str_replace(duration[i], "d"," days")
  duration[i] <-  str_replace(duration[i], "w"," weeks")
  report[i] <- paste0("<a href='", files.reports[i],"' target='_blank'>Link</a>")
}

# collect only tacc value
for (i in 1:ndata){
	tacc1[i] <- duration[i]
    tacc1[i] <-  str_remove_all(tacc1[i]," years")
    tacc1[i] <-  str_remove_all(tacc1[i], " hours")
    tacc1[i] <-  str_remove_all(tacc1[i], " days")
    tacc1[i] <-  str_remove_all(tacc1[i]," weeks")
}
tacc1 <- as.numeric(tacc1)

# Create time units vector

for (i in 1:ndata){
    if(str_detect(duration[i],"years")==TRUE){timeFormat1[i] <-"years"}
    if(str_detect(duration[i],"hours")==TRUE){timeFormat1[i] <-"hours"}
    if(str_detect(duration[i],"days")==TRUE){timeFormat1[i] <- "days"}
    if(str_detect(duration[i],"week")==TRUE){timeFormat1[i] <- "week"}
}

 # EXPOSURE ROUTE ####
    #read exposure route in data set

    # All dataset in a list
for (i in 1:ndata){
  # setwd(path)
  if(str_detect(files[i],".csv")){data[[i]] <-  read_delim(files[i],
                                                     delim = ";",
                                                     col_types = cols(),
                                                     escape_double = FALSE,
                                                     trim_ws = FALSE)}
  if(str_detect(files[i],".txt")){data[[i]] <- read_delim(files[i],
                                                      delim = "\t",
                                                      escape_double = FALSE, trim_ws = TRUE)}

  # select exposure route
 colname[[i]] <- colnames(data[[i]])

  if("expw" %in% colname[[i]]){exposure[[i]] <- c("water") }
    if("exppw" %in% colname[[i]]){exposure[[i]] <- c("pore water") }
      if("exps" %in% colname[[i]]){exposure[[i]] <- c("sediment") }
      if("expf" %in% colname[[i]]){exposure[[i]] <- c("food") }
  exposure <- unlist(exposure)



 # NUMBER OF POINTS ####
   # replicate
replicate[i] <- length(unique(data[[i]]$replicate)) #add condition by exp concentration
	 # concentration of exposure
  Cexp[[i]] <- data[[i]] %>%
		filter_all(any_vars(! is.na(.))) %>%
		filter(time != 0) %>%
		select(starts_with("exp"))

temp.Cexp <- data.frame(Cexp[[i]]) #temporary data frame instead of tibble for Cexp
factor.conc[[i]] <- levels(factor(temp.Cexp[,1])) #levels of exposure concentration


npoints[i] <- nrow(Cexp[[i]] %>% filter(Cexp[[i]] == factor.conc[[i]][1]))
npoint[i] <- paste0(npoints[i], " (",replicate[i],")")

 #add comments
  comments[i] <- c(names[[i]][5])
    # comments[i] <- str_replace_all(comments[i], "conc"," tested concentrations") #length(unique(Cexp)) or as.factor(Cexp)

   if("growth" %in% colnames(data[[i]])){comments[i] <- paste0(comments[i], "growth dilution")}

  # Metabolites ? ####
if("concm1" %in% colnames(data[[i]])){comments[i] <- paste0(comments[i],"biotransformation")} #number of metabolites?
  comments[i] <- str_replace_all(comments[i], "intermediate","intermediate size")
  comments[i] <- str_replace_all(comments[i], "small","small size")
  comments[i] <- str_replace_all(comments[i], "food","")
  comments[i] <- str_replace_all(comments[i], "sediment","")
  comments[i] <- str_replace_all(comments[i], "lipid","lipid fraction: 6.8%")
    # comments[i] <- str_replace_all(comments[i], "conc"," tested concentrations")
 if(length(factor.conc[[i]]) > 1){comments[i] <- paste0(comments[i], length(factor.conc[[i]])," tested concentrations")}

comments[i] <- str_replace_all(comments[i], "NA","")
}

 # CATEGORY for species ####
factor <- lapply(factor(species), levels)[[1]] # give all species
for (i in 1:ndata){
if("Apostichopus" %in% species[i]){category[i] <- c("marine invertebrate")}
if("Asellus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Axinella" %in% species[i]){category[i] <- c("seawater sponge")}
if("Brachydanio" %in% species[i]){category[i] <- c("fish")}
if("Calanus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Chaetopteryx" %in% species[i]){category[i] <- c("insect")}
if("Chironomus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Cloeon" %in% species[i]){category[i] <- c("insect")}
if("Chlorella" %in% species[i]){category[i] <- c("aquatic algae")}
if("Cyprinnodon" %in% species[i]){category[i] <- c("fish")}
if("Danio" %in% species[i]){category[i] <- c("fish")}
if("Daphnia" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Eisenia" %in% species[i]){category[i] <- c("aquatic worm")}
if("Ephemera" %in% species[i]){category[i] <- c("insect")}
if("Gammarus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Halophila" %in% species[i]){category[i] <- c("seawater plant")}
if("Heptagenia" %in% species[i]){category[i] <- c("insect")}
if("Hyalella" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Hydropsyche" %in% species[i]){category[i] <- c("insect")}
if("Lumbriculus" %in% species[i]){category[i] <- c("aquatic worm")}
if("Oncorhynchus" %in% species[i]){category[i] <- c("fish")}
if("Oryzias" %in% species[i]){category[i] <- c("fish")}
if("Physa" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Poecilus" %in% species[i]){category[i] <- c("insect")}
if("Radix" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Snail" %in% species[i]){category[i] <- c("terrestrial invertebrate")}
if("Solea" %in% species[i]){category[i] <- c("fish")}
if("Tubifex" %in% species[i]){category[i] <- c("aquatic worm")}
if("Planorbarius" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Enchytraeus" %in% species[i]){category[i] <- c("terrestrial worm")}
if("Gallus" %in% species[i]){category[i] <- c("vertebrate")}
if("Metaphire" %in% species[i]){category[i] <- c("aquatic worm")}
if("Mytilus" %in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Potamocorbula" %in% species[i]){category[i] <- c("marine invertebrate")}
if("Salmo" %in% species[i]){category[i] <- c("fish")}
if("Spirostomum" %in% species[i]){category[i] <- c("Heterotrichea")}
if("Tenebrio" %in% species[i]){category[i] <- c("insect")}
if("Tigriopus" %in% species[i]){category[i] <- c("marine invertebrate")}
if("Eisina" %in% species[i]){category[i] <- c("terrestrial worm")}
if("Anax"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Assellus"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Chaoborus"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Cloeon"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Culex"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Molanna"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Neocaridina"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Notonecta"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Parapoynx"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Plea"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Procambarus"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Rantra"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Sialis"%in% species[i]){category[i] <- c("aquatic invertebrate")}
if("Perca"%in% species[i]){category[i] <- c("fish")}

}


#  # CATEGORY for chemicals ####
# factor.chem <- lapply(factor(datatable_old$substance), levels)[[1]] # give all chemicals
# factor.chem
# 
# substance <- datatable_old$substance
# category.chem <- NULL
# for (i in 1:ndata){
# if(str_detect(substance[i],"pcb")==TRUE){category.chem[i] <- c("PCB")}
# if(str_detect(substance[i],"PCB")==TRUE){category.chem[i] <- c("PCB")}
# if("La" %in% substance[i]){category.chem[i] <- c("metal")}
# if(str_detect(substance[i],"HBCD")==TRUE){category.chem[i] <- c("flamme retardants")}
# if(str_detect(substance[i],"HCBD")==TRUE){category.chem[i] <- c("other")}
# if(str_detect(substance[i],"BDE")==TRUE){category.chem[i] <- c("flamme retardants")}
# if(str_detect(substance[i],"pyrene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"anthracene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"naphtalene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"fluoranthene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"phenanthrene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"phenantrene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"thracene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"uranium")==TRUE){category.chem[i] <- c("other")}
# if(str_detect(substance[i],"c14")==TRUE){category.chem[i] <- c("other")}
# if(str_detect(substance[i],"C14")==TRUE){category.chem[i] <- c("other")}
# if(str_detect(substance[i],"PRZ")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"propranolol")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"trimethoprim")==TRUE){category.chem[i] <- c("drug")} 
# if(str_detect(substance[i],"PFOS")==TRUE){category.chem[i] <- c("PFAS")} 
# if(str_detect(substance[i],"trans-")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"sulfadiazine")==TRUE){category.chem[i] <- c("drug")} 
# if(str_detect(substance[i],"tebuconazol")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"benzene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"sertraline")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"sertraline")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"SAmPAP")==TRUE){category.chem[i] <- c("PFAS")}
# if(str_detect(substance[i],"QCB")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"TPT")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"propiconazole")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"prochloraz")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"pentachlorophenol")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"chlorobenzene")==TRUE){category.chem[i] <- c("PCB")} 
# if(str_detect(substance[i],"PeCB")==TRUE){category.chem[i] <- c("PCB")}
# if(str_detect(substance[i],"PE")==TRUE){category.chem[i] <- c("nano-particule/microplastic")}
# if(str_detect(substance[i],"paroxetine")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"ofloxacin")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"mianserin")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"nano")==TRUE){category.chem[i] <- c("nano-particule/microplastic")}
# if(str_detect(substance[i],"malathion")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"imidacloprid")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"imidachloprid")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"hexachlorocyclohexane")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"hexylcyclohexane")==TRUE){category.chem[i] <- c("other")}
# if(str_detect(substance[i],"hCB")==TRUE){category.chem[i] <- c("PCB")}
# if(str_detect(substance[i],"HCE")==TRUE){category.chem[i] <- c("other")}
# if(str_detect(substance[i],"fluoxetine")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"fipronil")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"epoxiconazole")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"enrofloxacin")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"emodin")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"dodecane")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"diSPAP")==TRUE){category.chem[i] <- c("PFAS")}
# if(str_detect(substance[i],"dicofol")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"diclofenac")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"dichlorophenol")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"diazinon")==TRUE){category.chem[i] <- c("pesticide")} 
# if(str_detect(substance[i],"diazepam")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"cypermethrin")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"clarithromycin")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"chrysene")==TRUE){category.chem[i] <- c("hydrocarbon")}
# if(str_detect(substance[i],"chlorpyrifos")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"carbofuran")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"carbaryl")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"capture")==TRUE){category.chem[i] <- c("nano-particule")}  
# if(str_detect(substance[i],"bifenthrin")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"BaP")==TRUE){category.chem[i] <- c("hydrocarbon")}  
# if(str_detect(substance[i],"azoxistrobine")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"AZ")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"azithromycin")==TRUE){category.chem[i] <- c("drug")}
# if(str_detect(substance[i],"azinphos")==TRUE){category.chem[i] <- c("pesticide")} 
# if(str_detect(substance[i],"atrazine")==TRUE){category.chem[i] <- c("pesticide")}
# if(str_detect(substance[i],"aldicarb")==TRUE){category.chem[i] <- c("pesticide")} 
# if(str_detect(substance[i],"AgNP")==TRUE){category.chem[i] <- c("nano-particule")}
# if(str_detect(substance[i],"AgNO3")==TRUE){category.chem[i] <- c("nano-particule")}
# if(str_detect(substance[i],"AGNO3")==TRUE){category.chem[i] <- c("nano-particule")}
# if(str_detect(substance[i],"Ag2")==TRUE){category.chem[i] <- c("nano-particule")} 
# if(str_detect(substance[i],"diPAP")==TRUE){category.chem[i] <- c("PFAS")}
# if(str_detect(substance[i],"4-tert-octylphenol")==TRUE){category.chem[i] <- c("Octylphenols")}
# if(str_detect(substance[i],"4-nitrobenzyl-chloride")==TRUE){category.chem[i] <- c("other")} 
# if(str_detect(substance[i],"trichlorophenol")==TRUE){category.chem[i] <- c("pesticide")} 
# if(str_detect(substance[i],"aniline")==TRUE){category.chem[i] <- c("pesticide")}  
# if(str_detect(substance[i],"decane")==TRUE){category.chem[i] <- c("hydrocarbon")} 
# if(str_detect(substance[i],"DCB")==TRUE){category.chem[i] <- c("PCB")}
# if(str_detect(substance[i],"TCB")==TRUE){category.chem[i] <- c("PCB")}
# if(str_detect(substance[i],"TeCB")==TRUE){category.chem[i] <- c("PCB")}
# if("Ag" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Mn" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Cd" %in% substance[i]){category.chem[i] <- c("metal")}
# if("cd" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Cu" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Hg" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Ni" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Gd" %in% substance[i]){category.chem[i] <- c("metal")}
# if("Ce" %in% substance[i]){category.chem[i] <- c("metal")}
# }

```

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
fitPlot <- NULL
BAF.name <- NULL
BAF50 <- NULL
BAF2.5 <- NULL
BAF97.5 <- NULL

for (x in 1:ndata){
	i=x
	if(str_detect(files[i],".csv")){data[[i]] <-  read_delim(files[i],
                                                     delim = ";",
                                                     col_types = cols(),
                                                     escape_double = FALSE,
                                                     trim_ws = FALSE)}
  if(str_detect(files[i],".txt")){data[[i]] <- read_delim(files[i],
                                                      delim = "\t",
                                                      escape_double = FALSE, trim_ws = TRUE)}
filename <- files[i]
dataTable <- as_tibble(data[[i]])
tacc <- as.numeric(tacc1[i])
timeFormat <- timeFormat1[i] # Time unit
source("model_predict.r")
a <- print(paste0("Coffee is life!", x)) # check if everything is alright in the loop for calculations
		#generate the report
	# Variables for report
	concFileName <- files[x]
	nbReplicates <- as.numeric(replicate[x])
	# knit in format .PDF
	rmarkdown::render(input = "reportBIOACC_pdf.Rmd",
            output_format = "pdf_document")
a <- print(paste0("Hot coffee!", x)) # check if everything is alright in the loop for report
	file.rename(from="reportBIOACC_pdf.pdf",
              to=paste("reports/", file.name[x],".pdf", sep=""))
  # knit in format .HTML
	rmarkdown::render(input = "reportBIOACC_pdf.Rmd",
            output_format = "html_document")
	print(paste0("Hot coffee!", x)) # check if everything is alright in the loop for report
	file.rename(from="reportBIOACC_pdf.html",
              to=paste("reports/", file.name[x],".html", sep=""))


		if("exppw" %in% colnames(dataTable)){BAF.name[x] <- paste0("BCFpw")
BAF50[x] <- bcfpwMed
BAF2.5[x] <- 	bcfpwInf
BAF97.5[x] <- 	bcfpwSup
		}
	if("expw" %in% colnames(dataTable)){BAF.name[x] <- paste0("BCF")
BAF50[x] <- bcfMed
BAF2.5[x] <- bcfInf
BAF97.5[x] <-bcfSup
	}
	if("exps" %in% colnames(dataTable)){BAF.name[x] <- paste0("BSAF")
BAF50[x] <- bsafMed
BAF2.5[x] <- bsafInf
BAF97.5[x] <- bsafSup
	}
	if("expf" %in% colnames(dataTable)){BAF.name[x] <- paste0("BMF")
BAF50[x] <- bmfMed
BAF2.5[x] <- bmfInf
BAF97.5[x] <- bmfSup
	}

save(mcmc1, file=paste0(file.name[[x]],".RData"))
}

 BAF.table <- as.data.frame(cbind(BAF.name,BAF50,BAF2.5,BAF97.5))
 # write.csv(BAF.table,"BAF_table3.csv", row.names = FALSE)

# BAF
BAF <- NULL

for (i in 1:ndata){
  BAF[i] <- HTML(paste0(BAF.table[i,2]), "</br>", paste0("[",BAF.table[i,3]," - ",BAF.table[i,4],"]"))
}


```

```{r message=FALSE, comment=FALSE, warning=FALSE, echo = FALSE, include=FALSE}
#create the data frame

datatable <- NULL
datatable <- cbind.data.frame(dataset,paste0("<i>",species,"</i>"),  category, substance, duration, exposure, npoint, BAF, report, reference, comments)
colnames(datatable)<-c("dataset","genus","category", "substance", "duration of accumulation", "exposure route", "n (replicate)","Kinetic biaccumulation factor", "report", "reference", "comments")

 write.csv(datatable,"datatable_updte.csv", row.names = FALSE)
# View(datatable)

```

```{r echo=FALSE}
datatable <- read_csv("datatable_update.csv")

DT::datatable(datatable, escape = FALSE, rownames = FALSE, options = list( 
  order = list(list(1, 'asc')),
  pageLength=10,fixedHeader = TRUE, fixedHeader.header = TRUE, columnDefs =
                           list(list(className = 'dt-center',
                                     targets = 1:9))), extensions = 'FixedHeader')
```
